Sparse Function-space Representation \\ of Neural Networks

### 2023-05-23 paper/main.tex
updated rl intro

\section{\our for model-based reinforcement learning}
\label{app:rl}
In this appendix, we provide a background of the reinforcement learning problem, details of our
model-based RL algorithim, an overview of the cart pole swing up environment, and
all details of our experiments configuration for reproducibility.

more details of the reinforcement learning experiments, including
how we used \our in this setting.

>>>>

\section{\our for model-based reinforcement learning}
\label{app:rl}
In this appendix, we provide a background of the reinforcement learning problem, details of our
model-based RL algorithim, an overview of the cart pole swing up environment, and
all details required for reproducing our experiments.

% more details of the reinforcement learning experiments, including
% how we used \our in this setting.
